---
title: "Data Prep"
author: "Rapha?l Morsomme"
date: "February 11, 2020"
output: pdf_document
editor_options: 
  chunk_output_type: console
---

```{r setup}
library(tidyverse)
library(readr)
```

```{r read in data}
var <- read_table2("Data/Harvard_CAS_2001/Harvard_CAS_2001/DS0001/04291-0001-Record_layout.txt",
                   col_names = FALSE, skip = 9) %>%
  rename(var_name = X1, beg = X2, end = X3, type = X4) %>%
  select(-X5) %>%
  
  mutate(len = end-beg+1)


d <- read_fwf("data/Harvard_CAS_2001/Harvard_CAS_2001/DS0001/04291-0001-Data.txt",
         fwf_widths(widths = var$len, col_names = var$var_name),
         na = c(" ", "."),
         guess_max = 1e4)
```

## Response variables

We define **awareness** and **risk** scores, with the risk being disaggregated in three categories: consumption risk, behavioural risk and situational risks. A weighted sum of these three risks, appropriately scaled by student awareness, produces the global response variable **ressource_need** which measures how much a student might benefit from being presented with additional ressources.

### Awareness

```{r}
awareness = rowMeans(cbind(
  # School policy awareness
  rowMeans(cbind(d$B2==6, 
                 d$B3==5, 
                 d$B5 == 4), 
           na.rm=T),
  
  # Provided information
  rowMeans(cbind(d$B6A==1, 
                 d$B6B==1, 
                 d$B6C==1, 
                 d$B6D==1, 
                 d$B6E==1, 
                 d$B6F==1, 
                 d$B6G==1), 
           na.rm=T),
  
  # Educational material
  rowMeans(cbind(d$B7A==1, 
                 d$B7B==1, 
                 d$B7C==1, 
                 d$B7D==1, 
                 d$B7E==1), 
           na.rm=T)
), na.rm=TRUE)
```

### Consumption risk

```{r}
p_binge = recode(d$BINGE,
                 `0` = 0.1,
                 `1` = 0.9
                 )

p_freqbinge = recode(d$FREQBING,
                     `1` = 0.9,
                     `2` = 0.95
                     )

p_self_describe = recode(d$C7,
                         `1` = 0.05,
                         `2` = 0.9,
                         `3` = 0.1,
                         `4` = 0.2,
                         `5` = 0.3,
                         `6` = 0.5,
                         `7` = 0.9)

avg <- function(...) {
  args = c(...)
  args = args[!is.na(args)]
  p = length(args)
  1 - prod(1-args)^(1/p)
}
```

```{r}
consumption_risk = pmap_dbl(data.frame(p_binge, p_freqbinge, p_self_describe), avg)
```

### Behavioural risk

```{r}
# Survey questions C17 - C20 are not in the dataset....

```

### Situational risk

```{r}

p_insulted = recode(d$D1A,
                    `1` = 0.01,
                    `2` = 0.2,
                    `3` = 0.5,
                    `4` = 0.85)

p_assaulted = recode(d$D1C,
                    `1` = 0.1,
                    `2` = 0.9,
                    `3` = 0.99,
                    `4` = 0.999)

p_damage = recode(d$D1D,
                    `1` = 0.01,
                    `2` = 0.4,
                    `3` = 0.8,
                    `4` = 0.95)

p_advances = recode(d$D1H,
                    `1` = 0.1,
                    `2` = 0.9,
                    `3` = 0.99,
                    `4` = 0.999)

situational_risk = pmap_dbl(data.frame(p_insulted, 
                                       p_assaulted, 
                                       p_damage,
                                       p_advances), avg)
```

### Response variable

```{r}
ressource_need = (situational_risk + consumption_risk)*(1-awareness)

hist(ressource_need)
```

```{r variable}
d_cheap <- d %>% 
  mutate(Y = ressource_need,
         awareness = awareness,
         consumption_risk = consumption_risk,
         situational_risk = situational_risk) %>% 
  select(Y, # response
         awareness,
         consumption_risk,
         situational_risk,
         # predictors
         A1:A4A, A6,
         B2:B3, B16A:B16I, B22,
         F5,
         G1:G2, RACE, G12A:G13) %>%
  
  
  # code NA explicitly
  mutate(B2  = if_else(B2  == 6 , NA_real_, B2 ),
         B3  = if_else(B3  == 5 , NA_real_, B3 ),
         B22 = if_else(B22 == 5 , NA_real_, B22),
         F5  = if_else(F5  == 10, NA_real_, F5 )) %>%
  
  
  # categorical variables
  mutate_at(vars(A4, A4A, A6, B22, G1, G12B, G13),
            as.factor) %>%
  
  # keep variables with < 25% NA
  # removes A4A, B16A:B16J, B22
  select_if(function(x) mean(is.na(x)) < 0.25) %>%
  
  
  # Complete case analysis
  na.omit
```

```{r}
#save(data, file = "Data/data_model.RDATA")
save(d_cheap, file = "Data/data_model.RDATA")
```

