---
title: "Risk measure"
author: "Olivier Binette"
date: '2020-02-12'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(readr)
library(tidyverse)

var <- read_table2("../Data/Harvard_CAS_2001/Harvard_CAS_2001/DS0001/04291-0001-Record_layout.txt",
                   col_names = FALSE, skip = 9) %>%
  rename(var_name = X1, beg = X2, end = X3, type = X4) %>%
  select(-X5) %>%
  mutate(len = end-beg+1)

d <- read_fwf("../Data/Harvard_CAS_2001/Harvard_CAS_2001/DS0001/04291-0001-Data.txt",
         fwf_widths(widths = var$len, col_names = var$var_name),
         na = c(" ", "."),
         guess_max = 1e4) %>%
  select_if(function(x){mean(is.na(x)) < 0.1})
```

- Behavioural risk
- Situational risk

- Awareness score
- Alcohol risk

Challenges:
  - Complementary questions vs independent questions

Ideas: logistic model for probability of alcohol problem

Model of the -log((1-p)), p = prob(alcohol problem) or p = prob(benefit from ressources)

geometric average aggregation.

Group 1: Alcohol consumption (prob of alcohol problem)
  
  consumption:
    C1: # 5+ drinks
      C5 * C4 / p
    C2: # exactly 4 drinks
      4 * C2 / p
  
    p = 1-2^(C5 * C4 / a + 4*C2 / a)
    
Group 2: Behavioural risks

  Self-description:
    C7:
      Abstainer           0.05
      former problem      0.5
      infrequent drinker  0.1
      light drinker       0.2
      moderate drinker    0.3
      heavy drinker       0.5
      problem drinker     0.9
    
  last drink:
    C10
      never had     0.05
      not in last year  0.1
      not in the past 30 days   0.2
      not last week             0.25
      within the week           0.3
      
  

Group 3: Situational risks (prob to get in a problem situation related to alcohol)


```{R}
p_binge = recode(d$BINGE,
                 `0` = 0.1,
                 `1` = 0.9
                 )

p_freqbinge = recode(d$FREQBING,
                     `1` = 0.9,
                     `2` = 0.95
                     )

p_self_describe = recode(d$C7,
                         `1` = )
                         
```


```{r}
d %>%
  mutate(new = recode(BINGE,
                      ))
```

```{r}
avg <- function(...) {
  args = c(...)
  args = args[!is.na(args)]
  p = length(args)
  1 - prod(1-args)^(1/p)
}

score = pmap_dbl(data.frame(p_binge, p_freqbinge), avg) # d
```















